Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-15 draft.tex
fix; clean up face reflection

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{hyperref}         % For hypertext links

\input{header}

@@

@@

\begin{proof}
    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, 
    which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
    For $0 < m \leq M$, by the definition of shellability in Section~\ref{subsection:shellability}, 
    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
    where $\Minako_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.

    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
    \end{gather*}
    We define $w_{|T_0} := w_0$. 
    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
    This is true for $m = 1$. 
    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
    \begin{align} \label{equation:w''_ext_der}
        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\Minako_{m-1}}),
    \end{align}
    where $\Xi_{m} : T_{m} \rightarrow \Minako_{m-1}$ is the reflection mapping
    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
    \begin{align*}
        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
    \end{align*}
    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
    \begin{align*}
        \cartan w = \cartan u \text{ over } T_m,
    \end{align*}
    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
    \begin{align*}
        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
    \end{align*}

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        \leq  
        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
        + 
        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) = 0$, we have
    \begin{align*}
        \| u - \Xi_{m}^{\ast}(u_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
        + \| \cartan (\Xi_{m}^{\ast}(u_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})} )
        .
    \end{align*}
    We also use Proposition~\ref{proposition:pullbackestimate} to find 
    \begin{align*}
        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
        &\leq 
        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
        \| w \|_{L^{p}(\Minako_{m-1})}
        ,
        \\
        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
        &\leq 
        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
        ,
    \end{align*}
	\begin{align*}
        \| \Xi_{m}^{\ast}(w_{|\Minako_{m-1}}) \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
        \| w \|_{L^{p}(\Minako_{m-1})}
        ,
        \\
        \| \cartan (\Xi_{m}^{\ast}(w_{|\Minako_{m-1}})) \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\Minako_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
        \| \cartan u \|_{L^{p}(\Minako_{m-1})}
        ,
    \end{align*}
    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
\end{proof}

@@

        \item 
        % \todo{Combine all this to get the final transformation.}
        The last simplicial complex that we introduce is called $\calK$,
        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.

@@

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
% \usepackage[margin=0.1cm]{geometry}
\input{header}

\usepackage{xcolor}          % 
\usepackage{comment}          % 
\usepackage[colorlinks=true]{hyperref}         % For hypertext links
% Make the hyperlinks look similar to arXiv's
\hypersetup{
    colorlinks=true,
    linkcolor=Maroon,    % Color of internal links (sections)
    citecolor=red,    % Color of citations
    urlcolor=blue,     % Color for URLs
    urlbordercolor={1 1 1},
    pdfborder={0.5 0.5 0}  % Removes the border around the links
}
\usepackage{tikz-3dplot}      % 3d plots 
\usepackage{enumitem}
\setitemize[1]{left=0.0cm}

% Added by MV 
\usepackage{bm} % preferred version of bold symbols
\usepackage[normalem]{ulem} % for strikethrough (\sout) in collaborative writing
% \usepackage{cancel} % for strikethrough in collaborative writing (math formulas)
% \usepackage[textsize=tiny,color=blue!10!white]{todonotes}
% \newcommand{\todo}[1]{{\colorbox{yellow}{#1}}}
\setlength{\marginparwidth}{2cm}

\newcommand\cye[1]{%
\protect\leavevmode
\begingroup
    \color{blue}%
    #1%
\endgroup
}
% \color{red!35!yellow}

\newcommand{\mwl}[1]{{\color{red}#1}}
\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
\newcommand{\disk}{\cye{ball}}
\newcommand{\todo}[1]{{\color{RedOrange}\textbf{#1}}}

% LTeX: enabled=false
% Title, authors, and affiliations
% \title{Poincar\'e--Friedrichs constants over domains with shellable triangulations}
% \author{Th\'eophile Chaumont-Frelet, Martin Werner Licht, Martin Vohral\'ik}

\title{Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations}
\author{
    Th\'eophile Chaumont-Frelet\thanks{Inria Univ. Lille and Laboratoire Paul Painlev\'e, 59655 Villeneuve-d'Ascq, France, \texttt{theophile.chaumont@inria.fr}} \and
    Martin Werner Licht\thanks{\'Ecole Polytechnique F\'ed\'erale de Lausanne, CH-1015 Lausanne, Switzerland, \texttt{martin.licht@epfl.ch}} \and
    Martin Vohral\'ik\thanks{Inria, 48 rue Barrault, 75647 Paris, France \& CERMICS, Ecole des Ponts, 77455 Marne-la-Vall\'ee, France, \texttt{martin.vohralik@inria.fr}}
}
\date{}
% LTeX: enabled=true

@@

\tableofcontents

\section{Draft of the Reflection along faces in one of the first sections}

\begin{proof}
    %     This implies the determinant identity and estimate 
%     \begin{align*}
%         \det( \Jacobian \Xi ) 
%         = 
%         \frac 1 4 \left( (1+a)^2 - (1-a)^2 \right) 
%         &
%         = 
%         a
%         \leq 
%         \aspectratio(T_{1}) \aspectratio(T_{2}) 
%         .
%     \end{align*}
%     % Now we see that if $a \leq 1$, then $\sigma_{+} \leq 1 + c$, and if $a \geq 1$, then $\sigma_{+} \leq a + c$.
%     Suppose that $b, b' \in F$ and $\alpha, \alpha' \in \bbR$ such that $x = b + \alpha \hat h_0$ and $x' = b' + \alpha' \hat h_0$.
%     Since $\Xi(\hat h_0) = z_2$, it follows with the arguments as above and H\"older's inequality that 
%     \begin{align*}
%         \vecnorm{ \Xi(x) - \Xi(x') }
%         \leq  
%         \vecnorm{ b - b' } + | \alpha - \alpha' | \cdot \vecnorm{ z_2 }
%         \leq  
%         \vecnorm{ b - b' } + | \alpha - \alpha' | \aspectratio(T_1) \frac{\diam(T_2)}{\diam(T_1)} \vecnorm{ \hat h_0 }
%         \leq 
%         \left( 1 + \aspectratio(T_1)^2 \frac{\diam(T_2)^2}{\diam(T_1)^2} \right)^{\frac 1 2} \vecnorm{ x-x' }
%         .
%     \end{align*}
    \color{blue}
    \color{red}
    The linear mapping $\Xi$ takes the form 
    % Writing $\hat h_0$ for the unit normal in direction $z_1$, we have 
    \begin{align*}
        \Xi(x) 
        = 
        x 
        - \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_1
        + \frac{ \langle \hat h_0, x \rangle }{ \langle \hat h_0, z_1 \rangle } z_2
        ,
        \qquad 
        x \in \bbR^{n}
        .
    \end{align*}
    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
    By the Xu-Zikanatov estimate~\cite{xu2003some},
    \begin{align*}
        % \matnorm{ \Jacobian \Xi }
        \sigma_{+} 
        \leq 
        \frac{ \diam(T_1) }{ \height(T_1) }
        +
        \frac{ \diam(T_2) }{ \height(T_1) }
        \leq 
        \aspectratio(T_1) + \frac{ \diam(T_2) }{ \diam(T_1) } \aspectratio(T_2)
        .
    \end{align*}
    Analogous upper bound holds for $\sigma^{-1}_{-}$.
%     \begin{align}
%         \sigma_{-}^{-1} \leq \left( 1 + \aspectratio(T_1) \right) \aspectratio(T_2)
%     \end{align}
% \begin{comment}
    \color{Mulberry}
    \mwl{Tighter estimate via geometry}
    Matrix inverse lemma:
    \begin{align*}
        A ( A + (z_2-z_1) e_1^t )^{-1}
        =
        \Id
        - 
        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
        (z_2-z_1) e_1^t \cdot A^{-1}
        =
        \Id
        - 
        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
        (z_2-z_1) e_1^t \cdot A^{-1}
        .
    \end{align*}
    Putting in a multiple of $\alpha z_1$, we find 
    \begin{align*}
        \alpha z_1
        -
        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
        (z_2-z_1) 
        .
    \end{align*}

    Without loss of generality, $F$ lies in the hyperplane plane of the second to last coordinates,
    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
    We can write 
    \begin{align*}
        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
    \end{align*}
    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
    \begin{align*}
        A = 
        \begin{pmatrix}
            b_1/a_1 & 0 & 0
            \\
            (b_2-a_2)/a_1 & 1 & 0
            \\
            b_3/a_1 & 0 & 1
        \end{pmatrix}
        =:
        \begin{pmatrix}
            c_1 & 0 & 0
            \\
            c_2 & 1 & 0
            \\
            c_3 & 0 & 1
        \end{pmatrix}
    \end{align*}
    Its singular values are $1$ and 
    \begin{align*}
        \sigma_{\max}
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            +
            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
        }
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            +
            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        }
        =
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
        +
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        =
        \frac{1}{2}
        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
        +
        \frac{1}{2}
        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
        \leq 
        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
        .
    \end{align*}
    \begin{align*}
        \sigma_{\max}
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            -
            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
        }
        =
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
        -
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        .
    \end{align*}

    \begin{align*}
        \sigma_{\max}
        &= 
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
        \\&= 
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
            } }
        \\&= 
        \frac{1}{\sqrt 2}
        \sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
            }
        +
        \frac{1}{\sqrt 2}
        \sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
            }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
            }
        +
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
            }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
            }
        +
        \frac{1}{2}
        \sqrt{ 
            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
            }
        ,
        \\
        \sigma_{\min}
        &=
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
            }
        -
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
            }
        .
    \end{align*}
    It follows that 
    \begin{align*}
        \det \Jacobian\Xi
        &=
        \frac{1}{4}
        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
        +
        \frac{1}{4}
        \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
        \\
        \frac{1}{2} + \frac{1}{2} 
        .
    \end{align*}
    Matrix determinant lemma:
    \begin{align*}
        \det( A + (z_2-z_1) e_n^t ) = \left( 1 + e_n A^{-1} z_2 - e_n A^{-1} z_1 \right) \det(A)
        =
        \left( e_{n} A^{-1} z_2 \right) \det(A)
        =
        \frac{\langle \hat h, z_2 \rangle}{\langle \hat h, z_1 \rangle} \det(A)
        .
    \end{align*}
% \end{comment}
\end{proof}

\section{Material}

@@

\begin{proof}
    By assumption, there exists a shelling $T_0, T_1, \dots, T_{M}$. 
    We write $X_m := \cup_{j=0}^{m} T_j$, $0 \leq m \leq M$, 
    which is by Lemma~\ref{lemma:shell_triang_man} a triangulated $n$-dimensional submanifold with boundary. 
    For $0 < m \leq M$, by the definition of shellability in Section~\ref{subsection:shellability}, 
    $T_{m}$ and $X_{m-1}$ share the interface $\Gamma_{m}$, which is a collection of faces of $T_{m}$. 
    It follows from Lemma~\ref{lemma:existenceofstar} that adding $T_{m}$ completes a star in $\calT$ around the simplex $S_{m} \in \calT$, 
    where $\frakM_{m-1} \subseteq X_{m-1}$ is the complement of $T_{m}$ in that newly completed star.

    We will recursively construct $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$, satisfying the desired bound. 
    Let $u \in W^{p}\Alt^{k}(\Omega)$. 
    First, on $T_0$, from Lemma~\ref{lemma:PFexteriorsimplex}, 
    there exists $w_0 \in W^{p}\Alt^{k}(T_{0})$ satisfying $\cartan w_0 = \cartan u$ over $T_{0}$ together with 
    \begin{gather*}
        \| w_0 \|_{L^{p}(T_{0})} \leq C_{{\PF},k,T_{0},p} \| \cartan u \|_{L^{p}(T_{0})}.
    \end{gather*}
    We define $w_{|T_0} := w_0$. 
    Suppose now that $0 < m \leq M$ such that $w_{|X_{m-1}} \in W^{p}\Alt^{k}(X_{m-1})$ with $\cartan w = \cartan u$ over $X_{m-1}$. 
    This is true for $m = 1$. 
    We now define, as in Equations~(5.12) and~(5.14) of~\cite{ern2020stable} or Equations~(6.7) and~(6.9)~\cite{Chaum_Voh_p_rob_3D_H_curl_24},
    \begin{align} \label{equation:w''_ext_der}
        w_{|T_m} := u_{|T_m} + \Xi_{m}^{\ast}((w - u)|_{\frakM_{m-1}}),
    \end{align}
    where $\Xi_{m} : T_{m} \rightarrow \frakM_{m-1}$ is the reflection mapping
    as $\Xi_{1}$ in Proposition~\ref{proposition:starreflection} and the pullback is defined in~\eqref{equation:pullback}.
    Clearly, $w_{|T_m} \in W^{p}\Alt^{k}(T_{m})$. Moreover,
    \begin{align*}
        \trace_{\Gamma_{m}} w_{|T_m} = \trace_{\Gamma_{m}} w_{|X_{m-1}},
    \end{align*}
    since $u$ is trace continuous over $\Gamma_{m-1}$ and $\Xi_{m}$ is the identity along $\Gamma_{m-1}$, and
    \begin{align*}
        \cartan w = \cartan u \text{ over } T_m,
    \end{align*}
    since $\cartan w = \cartan u$ over $X_{m-1}$ and $\Xi_{m}^{\ast}$ preserves this. Thus
    \begin{align*}
        w_{|X_{m}} \in W^{p}\Alt^{k}(X_{m}) \text{ with } \cartan w_{m} = \cartan u \text{ over } X_{m}. 
    \end{align*}

    We want to estimate norms. 
    By construction,
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        \leq  
        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
        + 
        \| u - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Due to Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative}, since $\trace_{\Gamma_{m-1}} (u_{|T_m} - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}})) = 0$, we have
    \begin{align*}
        \| u - \Xi_{m}^{\ast}(u_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{\PF,T_{m},\Gamma_{m},k,p} (\| \cartan u      \|_{L^{p}(T_{m})} 
        + \| \cartan (\Xi_{m}^{\ast}(u_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})} )
        .
    \end{align*}
    We also use Proposition~\ref{proposition:pullbackestimate} to find 
    \begin{align*}
        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
        &\leq 
        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
        \| w \|_{L^{p}(\frakM_{m-1})}
        ,
        \\
        \| \cartan (\Xi_{m}^{\ast}(w_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})}
        &\leq 
        \|\det(\Jacobian \Xi_{m}  )\|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
        \| \cartan u \|_{L^{p}(\frakM_{m-1})}
        ,
    \end{align*}
	\begin{align*}
        \| \Xi_{m}^{\ast}(w_{|\frakM_{m-1}}) \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k}_{L^{\infty}(T_{m})}
        \| w \|_{L^{p}(\frakM_{m-1})}
        ,
        \\
        \| \cartan (\Xi_{m}^{\ast}(w_{|\frakM_{m-1}})) \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi_{m}  )|^{-\frac 1 p}_{L^{\infty}(\frakM_{m-1})} 
        \| \Jacobian \Xi_{m} \|^{k+1}_{L^{\infty}(T_{m})}
        \| \cartan u \|_{L^{p}(\frakM_{m-1})}
        ,
    \end{align*}
    where we have employed that $\cartan w = \cartan u$ over $X_{m-1}$. 
    Using the properties of the reflection mapping in Proposition~\ref{proposition:starreflection}, the desired recursive estimate follows. 
\end{proof}

@@

\begin{itemize}
        \item 
        % \todo{Combine all this to get the final transformation.}
        The last simplicial complex that we introduce is called $\calK$,
        and it is the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$.

@@

\end{itemize}
